|

### 2021-07-21 prova_knit_finale.Rmd
commit

Since we do not have access to the exact filtering distribution of the SV model, when assessing how rapidly different particle filters converge to it, we actually need to approximate even such target distribution as to have a benchmark.\
Fortunately, convergence results about particle filters ensure that when the number of particles diverges, the approximation converges to the target distribution.\footnote{Molto probabilmente la frase formulata così non è formalmente corretta...bisognerebbe fare riferimento alla sezione sulla convergenza. Inoltre, va chiarito il punto della "doppia convergenza" per T e per N (ossia, se il nostro T sia sufficientemente alto da parlare di convergenza quando N è molto grande).} Thus, we run one of the particle filters with a very large number of particles, and assume that such approximation is close enough to the target to be used itself as the distribution the filters should tend to.\
With such a benchmark, we can then compare how different filters approach it as the number of particles increases. We employ the Root Mean Squared Error and the Mean Absolute Error to measure discrepancies from the benchmark. Note that the Liu and West filter can not be included in such an analysis: trivially, the comparison assumes that the competing algorithms are approximating the same target distribution.\footnote{For an analogous reason, we do not need to conduct this analysis on all the indices, but we can rather focus on one, the SP500. Indeed, what matters in this section is not how well the model fits the data, but rather how different algorithms approach the same distribution yielded by the same model on a given set of data.}

>>>>

Since we do not have access to the exact filtering distribution of the SV model, when assessing how rapidly different particle filters converge to it, we actually need to approximate even such target distribution as to have a benchmark.\
Fortunately, convergence results about particle filters ensure that when the number of particles diverges, the approximation converges to the target distribution.\footnote{Molto probabilmente la frase formulata così non è formalmente corretta...bisognerebbe fare riferimento alla sezione sulla convergenza. Inoltre, va chiarito il punto della "doppia convergenza".} Thus, we run one of the particle filters with a very large number of particles, and assume that such approximation is close enough to the target to be used itself as the distribution the filters should tend to.\
With such a benchmark, we can then compare how different filters approach it as the number of particles increases. We employ the Root Mean Squared Error and the Mean Absolute Error to measure discrepancies from the benchmark. Note that the Liu and West filter can not be included in such an analysis: trivially, the comparison assumes that the competing algorithms are approximating the same target distribution.\footnote{For an analogous reason, we do not need to conduct this analysis on all the indices, but we can rather focus on one, the SP500. Indeed, what matters in this section is not how well the model fits the data, but rather how different algorithms approach the same distribution yielded by the same model on a given set of data.}
